SVG: The Paper

### 2022-06-06 Analysis/index.Rmd
changing figure size
init sel model

We can model this as multi-level Gaussian? Yes, although it seems like people are in one of two clusters.

@@

m <- readRDS("scratch/init_sel_model.rds")
z <- seq(0, 1, 0.01)

gather_draws(m, u[dim, observer]) %>% 
  ungroup() %>%
  select(-.variable) %>%
  rename(obs_b = ".value") %>%
  full_join(gather_draws(m, b[dim]),
             by = c("dim", ".chain", ".iteration", ".draw")) %>%
  mutate(obs_b = .value + obs_b,
         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a

a %>% group_by(observer, param, dim) %>%
  summarise(value = mean(obs_b) , .groups = "drop") %>%
  pivot_wider(names_from = param, values_from = value) %>%
  rename(mean = "mu") -> am

@@

  pmap(filter(am,  dim == dm) %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
    set_names(rownames(filter(am,  dim == dm))) %>%
    bind_rows() %>%
    mutate(z = z) %>%
    pivot_longer(-z, names_to = "observer", values_to = "v") %>%
    ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
    scale_x_continuous(dm) + scale_y_continuous("likelihood") -> plt

@@

create_post_plot("x") + create_post_plot("y")
```

- Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?

Do participants who differ in terms of their initial target selection differ in other ways too?

```{r echo = TRUE, fig.cap = "Whether participants have a central or corner bias for the intiial target selection appears to be largely independent of their other model parameters."}
full_join(fit, filter(am, dim == "x"), by = "observer") %>%
  pivot_longer(c(pA, pS, bP, bM, accuracy), 
               names_to = "statistic", values_to = "value") %>%
  mutate(intial_sel = if_else(mean < 0, "corner", "central")) %>%
  ggplot(aes(statistic, value, fill = intial_sel)) +
  geom_boxplot(alpha = 0.5) + 
  facet_wrap(~statistic, scales = "free", nrow = 1) +
  theme(legend.position = "bottom") + 
   scale_fill_manual("intial target selection",
                     values = c(col3[2], col3[3]))
```

>>>>

## Multi-level Model

We can model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters.

@@

m <- readRDS("scratch/init_sel_model.rds")

gather_draws(m, u[dim, observer]) %>% 
  ungroup() %>%
  select(-.variable) %>%
  rename(obs_b = ".value") %>%
  left_join(gather_draws(m, b[dim]), 
            by = c("dim", ".chain", ".iteration", ".draw")) %>%
  mutate(obs_b = exp(.value + obs_b),
         .variable = if_else(dim %in% c(1,2), "a", "b"),
         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
  select(observer, dim, .iteration, obs_b, param = ".variable") -> a

a %>% group_by(observer, param, dim) %>%
  summarise(value = mean(obs_b) , .groups = "drop") %>%
  pivot_wider(names_from = param, values_from = value) -> am

compute_beta_dist <- function(observer, a, b) {
  x <- seq(0.01,0.99,0.01)
  return(tibble(observer = observer, 
                x=  x,
                z = dbeta(x, a, b)))

}

@@

   pmap_df(filter(am,  dim == dm) %>% select(observer, a, b), 
                      compute_beta_dist) %>%
    ggplot(aes(x = x, y = z, group = observer)) + 
    geom_path(alpha = 0.25) +
    scale_x_continuous(dm) + 
    scale_y_continuous("likelihood") -> plt

@@

create_post_plot("x") + create_post_plot("y") 
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

## Mixture Model

It looks like we can simplify the model somewhat by using a two component mixture model instead!

```{r, fig.height = 6, fig.cap = "(*top*) Beta distributions for $x$ and $y$ coordinated"}

m <- readRDS("scratch/init_sel_model2.rds")

sample_beta <- function(c, .draw, dim, a, b) {
  x <- seq(0.01, 0.99, 0.01)
  return(tibble(c = c, 
                draw = .draw,
                dim = dim,
                x = x,
                z = dbeta(x, shape1 = a, shape2 = b)))
}

gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c], ndraws = 100) %>%
  separate(.variable, into = c("param", "dim")) %>%
  select(-.chain, -.iteration) %>%
  pivot_wider(names_from = param, values_from = ".value") %>%
  pmap_df(sample_beta) %>%
  mutate(c = as_factor(c)) -> plt_dat

plt_dat %>% filter(dim == "x") %>%
  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
  geom_path(alpha = 0.1) + 
  facet_wrap(~dim) + 
  theme(legend.position = "none") -> plt_x

plt_dat %>% filter(dim == "y") %>%
  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
  geom_path(alpha = 0.1) + 
  facet_wrap(~dim) + 
  theme(legend.position = "none") +
  scale_x_continuous("y") -> plt_y

gather_draws(m, lambda[observer]) %>%
  ggplot(aes(.value, group = observer)) + 
  geom_density(alpha = 0.25, fill = "grey") -> plt_lambdas

(plt_x + plt_y) / plt_lambdas
